Relationships in the extremes and their influence on competition and coexistence

### 2022-01-06 paper/Paper.Rnw
edditing methods and results, added modified fig6

%***DAN: Methods paras here for G4, if we accomplish G4
To achieve goal G4 from the Introduction, i.e., to provide an empirical example of species coexistence which highlights the role ATAs can play, we consider the coexistence of diatom species in chemostat batch experiments by \cite{Descamps_2005}. In their experiments, measurements of growth of \emph{Cyclotella pseudostelligera} and \emph{Fragilaria crotonensis} over a range of temperatures was used to parametrize a competitive resource model as follows:
put model here
\cite{Descamps_2005} used simulations to show that coexistence occurs with oscillating temperature fluctuations with parameters $\theta_0 = 18, a = 6, P = 60$d and \cite{Ellner_2016, Ellner_2019} broke down their coexistence into the contrirbuting mechanisms. Here, we consider varying parameters of temperature fluctuations and further decompose the coexistence of \emph{C. pseudostelligera} and \emph{F. crotonensis} to account for contributions of ATAs and ATA effects as described above. Our decomposition is defined by $E(t)=\theta(t)$, $C_j(t)=(K_j(t)+S(t))/S(t)$ and $r_j(E_j,C_j)=\frac{V_j(E)}{C_j} -D$. We first considered the scenario where \emph{F. crotonensis} is the invader and emph{C. pseudostelligera} is the resident to compute the coexistence decomposition for \emph{F. crotonensis}.

Like for G2, we first plotted the terms of equation \ref{eq:full_decomp} for the chemostat model against independent parameters defining temperature oscillation, $\theta_0, a$, and $P$, a total of three plots. For each plot, we set two of the parameters constant at the original parameters which coexistence was experimentally found in \cite{Descamps_2005}, and let the remaining temperature parameter vary. 
We let $\theta_0$ vary in $[16,19]$, $a$ vary in $[1,6]$, and $P$ vary in $[20,120]$. 
Relative importance of contributions was judged from the 
plots to assess whether and to what extent ATA effects on coexistence were meaningfully large for the lottery model, compared to 
the contributions of other mechanisms. 
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).

To further explore the parameter space, we generated two dimensional surface plots which reveal the subsets of parameter space where coexistence is possible with ranging degrees of ATA contributions and where ATA rescue occurs. We evaluated coexistence under two varying parameters and indicated $\Delta_i^{[EC]}/\text{IGR}$, a ratio of ATA contribution to total IGR, with a color bar and contour lines. Positive values of $\Delta_i^{[EC]}/\text{IGR}$ indicate coexistence and negative values indicate failure of coexistence. Greater magnitudes of $\Delta_i^{[EC]}/IGR$ and higher color intensity indicate greater contribution of ATAs to the IGR and positive cases where $\Delta_i^{[EC]}>IGR$ indicate ATA rescue.

@@

>>>>

%***DAN: Methods paras here for G4, if we accomplish G4
To achieve goal G4 from the Introduction, i.e., to provide an empirical example of species coexistence which highlights the role ATAs can play, we consider the coexistence of diatom species established by chemostat batch experiments \citep{Descamps_2005}. \citep{Descamps_2005} used measurements of growth of \emph{Cyclotella pseudostelligera} and \emph{Fragilaria crotonensis} over a range of temperatures to parametrize a competitive resource model as follows:
put model here
Via simulations, \cite{Descamps_2005} showed that coexistence of \emph{C. pseudostelligera} and \emph{F. crotonensis} occurs with oscillating temperature fluctuations, $\theta(t)=\theta_0 (t) +  a\sin(2\pi t/P)$, defined by parameters $\theta_0 = 18, a = 6, P = 60$d. \cite{Ellner_2016, Ellner_2019} broke down their coexistence into the contrirbuting mechanisms, and here, we consider varying parameters of temperature fluctuations and further decompose the coexistence of \emph{C. pseudostelligera} and \emph{F. crotonensis} to account for contributions of ATAs and ATA effects as described above. Our decomposition is defined by $E(t)=\theta(t)$, $C_j(t)=(K_j(t)+S(t))/S(t)$ and $r_j(E_j,C_j)=\frac{V_j(E)}{C_j} -D$. We first considered the scenario where \emph{F. crotonensis} is the invader and emph{C. pseudostelligera} is the resident to compute the coexistence decomposition for \emph{F. crotonensis}. 
%put reverse in sup mat?
Like for G2, we first plotted the terms of equation \ref{eq:full_decomp} for the chemostat model against independent parameters defining temperature oscillation, $\theta_0, a$, and $P$, a total of three plots. For each plot, we set two of the parameters constant at the original parameters which coexistence was experimentally found in \cite{Descamps_2005}, and let the remaining temperature parameter vary. 
We let $\theta_0$ vary in $[16,19]$, $a$ vary in $[1,6]$, and $P$ vary in $[20,120]$. 
Relative importance of contributions was judged from the 
plots to assess whether and to what extent ATA effects on coexistence were meaningfully large for the lottery model, compared to 
the contributions of other mechanisms. 
The simulation methods of \cite{Ellner_2019} were used to compute the components of (\ref{eq:full_decomp}).

To further explore the parameter space, we generated two dimensional surface plots which reveal the subsets of parameter space where coexistence is possible with ranging degrees of ATA contributions and where ATA rescue occurs. We evaluated coexistence under two varying parameters and indicated $\Delta_i^{[EC]}/\text{IGR}$, a ratio of ATA contribution to total IGR, with a color bar and contour lines. Greater magnitudes of $\Delta_i^{[EC]}/IGR$ and higher color intensity indicate greater contribution of ATAs to the IGR and positive cases where $\Delta_i^{[EC]}>IGR$ indicate ATA rescue.

@@

Fig.\ref{fig:fig6} displays the subsets of environmental parameters for which coexistence occurs or fails and the degree of ATA contribution to the IGR. Specific to this model and parameter ranges, because $\Delta_i^{[EC]}$ is always positive, all positive values of $\Delta_i^{[EC]}/\text{IGR}$ indicate coexistence and negative values of $\Delta_i^{[EC]}/\text{IGR}$ indicate failure of coexistence. Futhermore, ATA exlusion does not occur and ATA rescue occurs in positive cases where $\Delta_i^{[EC]}>IGR$. To preserve simplicity and readibility of the plots, |$\Delta_i^{[EC]}/\text{IGR}$>1| were capped at |1|.
